Stable Neo-Hookean Flesh Simulation

### 2019-11-07 LaTeX-Master-Vorlage/chapter/Background.tex
working on background, material constants

\begin{definition}[\textbf{Singular Values}]
The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
\end{definition}

@@

\begin{theorem}[\textbf{The SVD Theorem}]
Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices U $\in$ $\mathbb{R}^{m x m}$, V $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\tilde{\Sigma}$ $\in$ $\mathbb{R}^{m x n}$ such that

@@

\end{theorem}
Reference: \cite{ford2014numerical}, chap. 15

@@

@@

\subsection{Material Constants}
When we look at a deformation of an object we need to consider the material the object consists of. A material can be very stiff like steel or easily deformable ones like robber.

@@

\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)} \in [-1, 0.5] \]

The poisson's ratio is of importance for us because it characterizes the materials resistance to volume change. Usually the poisson's ratio of a material is positive. A negative value would mean that the material becomes wider in the cross section when it is stretched. This behaviour is very uncommon in nature. Here are some examples of the poisson's ratio of common materials:

\begin{table}[h!]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    Material & Poisson's ratio \\ \hline
    rubber & 0.4999 \\ \hline
    titanium & 0.265-0.34 \\ \hline
    glass & 0.18–0.3 \\ \hline
    cork & 0.0 \\ \hline
    \end{tabular}
    \caption{Different materials with their poisson's ratio}
\label{table:1}
\end{table}

>>>>

\begin{definition}[\textbf{Singular Values}]
\label{singular_values}
The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
\end{definition}

@@

\begin{theorem}[\textbf{The SVD Theorem}]
\label{SVD}
Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices U $\in$ $\mathbb{R}^{m x m}$, V $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\tilde{\Sigma}$ $\in$ $\mathbb{R}^{m x n}$ such that

@@

\end{theorem}
The definition and theorem were taken from \cite{ford2014numerical} (def. \ref{SVD} S.113, thm. \ref{singular_values} S.300).

@@

\begin{theorem}[\textbf{The Polar Decomposition Theorem}]
\label{PD}

Let \textbf{F} be a non-singular square matrix. Then \textbf{F} can be decomposed uniquely into either of the following two products
\[
\boldsymbol{F} = \boldsymbol{RU}, \quad \boldsymbol{F} = \boldsymbol{VR}
\]
where \textbf{R} is orthogonal and \textbf{U} and \textbf{V} are positive definite symmetric matrices.
\end{theorem}

A matrix \textbf{A} is positive definite if $\textbf{x}^{T}\textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.

The definition and theorem were taken from \cite{Spencer1980} (thm. \ref{PD} S.12).

@@

\subsection{Material Constants}
When we look at a deformation of an object we need to consider the material the object consists of. A material can be very stiff like steel or easily deformable like rubber. In order to measure the deformation in a specific material we need the \textit{Poisson's Ratio} of said material. The poisson's ratio is a material constant that is defined as

\[
	\sigma = - \frac{\epsilon_{11}}{\epsilon_{22}} \in [-1, 0.5]
\]

where $\epsilon_{11}$ is the lateral and $\epsilon_{22}$ the axial strain. The range in which $\sigma$ lies in starts at $-1$ and goes up to $0.5$ \cite{PhysRevB.80.132104}. Usually the poisson's ratio of a material is positive. A negative value would mean that the material becomes wider in the cross section when it is stretched. This behaviour is very uncommon in nature. In our use case we need the poisson's ratio as a characterization for the resistance to volume change of a given material.

Here are some examples of the poisson's ratio of various materials:

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Material} & \textbf{Poisson's ratio} \\ \hline
    C (graphite) & 0.31 \\ \hline
    Sn (metal) & 0.357 \\ \hline
    Cu & 0.355 \\ \hline
    Zn & 0.25 \\ \hline
    Ag & 0.36 \\ \hline
    Au & 0.45 \\ \hline
    Concrete & 0.20–0.37 \\ \hline
    Titanium (dental alloy) & 0.30–0.31 \\ \hline
    Bronze & 0.34 \\ \hline
    18–8 Stainless steel & 0.305 \\ \hline
    Natural rubber & 0.4999 \\ \hline
	B\textsubscript{2}O\textsubscript{3} glass & 0.30 \\ \hline
	GeO\textsubscript{2} glass & 0.20 \\ \hline	
    \end{tabular}
    \caption{Different materials with their poisson's ratio taken from \cite{PhysRevB.80.132104}}
\label{table:1}
\end{table}

@@

\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)}  \]
